Quotients of the magmatic operad:\\ lattice structures and convergent rewrite systems

### 2018-09-10 Conclusion.tex
Fin relecture Cyrille
Relecture conclusion

A first research direction consists in finding convergent presentations
for (all or most of) the $\CAs{\gamma}$ operads in
order to describe algebraic and combinatorial properties of these
operads (as describing explicit bases, computing Hilbert
series, and providing combinatorial realizations). This has been
done only in the case $\gamma = 3$. For some other cases, we only have
conjectural and experimental data (see Section~\ref{?}).
\Todo{S: compléter avec la bonne partie une fois qu'on aura ajouté ces
données}.
\medbreak

@@

A third axis consists in studying if the completion of presentations of
quotients of the magmatic operad maintains links with
the lattice structure introduced in Section~\ref{sec:Magmatic_operads}.
More precisely, assuming that we have completed the presentations of
the quotients $\Oca_1$ and $\Oca_2$ of $\Mag$,
as well as the one of the lower-bound $\Oca_2 \InfQMag \Oca_2$, the
question consists in designing an algorithm for computing a completion
of a presentation of the upper-bound
$\Oca_1 \SupQMag \Oca_2$. Of course, the same question also makes sense
for the lattice of comb associative operads introduced in
Section~\ref{sec:CAs_d}.
\medbreak

@@

A last research axis rely on the study on the $2$-magmatic operad
$\TwoMag$, that is, the free operad generated by two binary elements.
The analog of the associative operad in this context is the operad
$\TwoAs$ (see~\cite{LR06}), defined as the quotient of $\TwoMag$ by
the congruence saying that the two generators are associative. This
operad has a nice combinatorial realization in terms of alternating
bicolored Schröder trees. The question consists here in generalizing
our main results for the quotients of $\TwoMag$ and the generalizations
of $\TwoAs$ (definition of analog of comb associative operads and
study of its presentations).
\medbreak

>>>>

A first research direction consists in finding convergent presentations
for (all or most of) the operads $\CAs{\gamma}$ in
order to describe algebraic and combinatorial properties of them (as
describing explicit bases, computing Hilbert series, and providing
combinatorial realizations). This has been done only in the case
$\gamma = 3$. For some other cases, we only have conjectural and
experimental data (see
Section~\ref{sec:higher_comb_associative_operads}).
\medbreak

@@

A third axis consists in studying if the completion of presentations of
quotients of the magmatic operad maintains links with
the lattice structure introduced in Section~\ref{sec:Magmatic_operads}.
More precisely, assuming that we have completed the presentations of
the quotients $\Oca_1$ and $\Oca_2$ of $\Mag$,
as well as the one of the lower-bound $\Oca_1 \InfQMag \Oca_2$, the
question consists in designing an algorithm for computing a completion
of a presentation of the upper-bound
$\Oca_1 \SupQMag \Oca_2$. Of course, the same question also makes sense
for the lattice of comb associative operads introduced in
Section~\ref{sec:CAs_d}.
\medbreak

@@

A last research axis relies on the study on the $2$-magmatic operad
$\TwoMag$, that is, the free operad generated by two binary elements.
The analog of the associative operad in this context is the operad
$\TwoAs$~\cite{LR06} defined as the quotient of $\TwoMag$ by the
congruence saying that the two generators are associative. This operad
has a nice combinatorial realization in terms of alternating bicolored
Schröder trees. The question consists here in generalizing our main
results for the quotients of $\TwoMag$ and the generalizations of
$\TwoAs$ (that is, the definition of analogs of comb associative operads
and the study of their presentations).
\medbreak
